---
title: "Plots for test experiment"
output:
  html_document:
    df_print: paged
---

## Preamble

```{r}
library(DBI)
library(RSQLite)
library(dplyr)
library(ggplot2)
library(stringr)
```

## Connect to DB and load summary across replicates at final timepoint

```{r}
L <- 200
L2 <- L * L

# The body is inside a function that gets executed once.
# The purpose of this trick is to limit the scope of temporary variables:
# they only exist inside the function.
# (`db_conn` and `runs` do not exist after running this code.)
output_last <- (function() {
  db_conn <- dbConnect(SQLite(), 'db.sqlite')
  runs <- dbGetQuery(db_conn,
    'SELECT run_id, productivity_function_FH AS prod_func, max_rate_FH, frac_global_FH, max_rate_AD, min_rate_frac_AD, rate_DF FROM runs'
  )
  
  df <- dbGetQuery(db_conn,
    'SELECT run_id, H, A, F, D, H_lifetime_avg, A_lifetime_avg, F_lifetime_avg,D_lifetime_avg, beta_mean FROM output WHERE time = 150.0'
  ) %>%
    left_join(runs, by = 'run_id') %>%
    mutate(H = H / L2, A = A / L2, F = F / L2, D = D / L2)
  dbDisconnect(db_conn)
  
  df
})()

summary <- output_last %>%
  group_by(prod_func, max_rate_FH, frac_global_FH, max_rate_AD, min_rate_frac_AD, rate_DF) %>%
  summarize(H = mean(H), A = mean(A), F = mean(F), D = mean(D), 
            beta_mean = mean(beta_mean),
            H_lifetime_avg=mean(H_lifetime_avg),
            A_lifetime_avg=mean(A_lifetime_avg),
            F_lifetime_avg=mean(F_lifetime_avg),
            D_lifetime_avg=mean(D_lifetime_avg)
            )
```

## Plot function

This function constructs `facet_wrap` code (via string formatting) for a particular parameter
on the x axis and a particular measurement on the y axis, and then executes it
(via `eval(parse(...))`).

All combinations of other parameters are used as facet variables.

Plots are saved as `{y_var}_{x_var}.pdf` in the `plots` directory.

```{r}
if(!dir.exists('plots')) {
  dir.create('plots')
}
x_vars <- c('max_rate_FH', 'frac_global_FH', 'max_rate_AD', 'min_rate_frac_AD', 'rate_DF')
y_vars <- c('beta_mean', 'H', 'A', 'F', 'D','H_lifetime_avg','A_lifetime_avg','F_lifetime_avg','D_lifetime_avg')
plot_relationship <- function(x_var, y_var) {
  x_vars_str = paste(x_vars[x_vars != x_var], collapse = ', ')
  p <- eval(parse(text = str_glue(
    "ggplot(output_last, aes(x = factor({x_var}), y = {y_var}, color = prod_func)) +
      geom_boxplot(outlier.size = 0) +
      geom_point(position=position_jitterdodge(), size = 0.1) +
      facet_wrap(vars({x_vars_str}), ncol = 8, labeller = labeller(.rows = label_both)) +
      xlab('{x_var}') +
      ylab('{y_var}')
    "
  )))
  
  n_combos = nrow(summary) / length(unique(unlist(summary[, x_var]))) / 2
  n_rows = ceiling(n_combos / 8)
  
  ggsave(
    file.path('plots', str_glue('{y_var}-{x_var}.pdf')), p,
    width = 20, height = 20 * n_rows / 8
  )
  p
}
```


## Plot all x_var vs. y_var relationships

```{r}
for(x_var in x_vars) {
  for(y_var in y_vars) {
    plot_relationship(x_var, y_var)
  }
}
```
